---
title: "Northrop Grumman CATTConV Survey Results"
output: github_document
always_allow_html: true
---

```{r setup, include=FALSE}
library(readxl)
library(DT)
library(Rmisc)
library(tidyverse)
library(knitr)
library(ggcorrplot)
library(corrplot)
library(stringr)
library(tm)
library(qdap)
library(wordcloud)
library(wordcloud2)
library(RColorBrewer)
library(data.table)
library(ggdendro)
library(factoextra)
library(randomForest)


df<- read_excel("CATTConSurveyResults.xls")

#Add id to each row
df<-df %>% drop_na(CyberPro)
df<- df %>% mutate("ID"=rownames(df))

#Reverse Scores for select columnn
columnsToReverse <-  c('Skepticism13', 'Skepticism14', 'Skepticism15', 'Skepticism16','Skepticism17', 'Skepticism21', 'Skepticism22', 'Skepticism24', 'Curiosity11','Curiosity12','Curiosity13','Curiosity14', 'Curiosity15', 'NeedCognition3','NeedCognition4', 'NeedCognition5', 'NeedCognition7', 'NeedCognition9', 'NeedCognition12', 'NeedCognition16', 'NeedCognition17', 'SelfRegulation6', 'SelfRegulation9', 'SelfRegulation13', 'SelfRegulation17', 'SelfRegulation23', 'NonConformity2', 'NonConformity4', 'NonConformity5', 'NonConformity7', 'NonConformity9', 'Adaptability2', 'Adaptability5', 'Adaptability6','Adaptability7','Adaptability8', 'Grit1', 'Grit3', 'Grit5', 'Grit6')

df[,columnsToReverse] <- 7-df[, columnsToReverse]

#Raw Scoring
dfa <- df %>% group_by(ID) %>%  
     mutate("SearchforKnowledge" = (sum(Skepticism1,Skepticism2,Skepticism3,Skepticism4,Skepticism5,Skepticism6) / 36) ,      
      "SuspensionofJudgement" = (sum(Skepticism7, Skepticism8,Skepticism9,Skepticism10,Skepticism11)/ 30), 
     "SelfDetermining" = (sum(Skepticism13,Skepticism14,Skepticism15,Skepticism16,Skepticism17) / 30) , #Removed Skepticism12
     "InterpersonalUnderstanding" = (sum(Skepticism18, Skepticism19,Skepticism20,Skepticism21,Skepticism22) / 30) , 
     "SelfConfidence" = (sum(Skepticism23, Skepticism24,Skepticism25,Skepticism26,Skepticism27) / 30) , 
     "QuestioningMind" = (sum(Skepticism28, Skepticism29, Skepticism30)/ 18) , 
     "JoyousExploration" = (sum(Curiosity1,Curiosity2,Curiosity3,Curiosity4,Curiosity5) / 30) , 
     "DeprivationSensitivity" = (sum(Curiosity6,Curiosity7,Curiosity8,Curiosity9,Curiosity10) / 30) , 
     "StressTolerance" = (sum(Curiosity11,Curiosity12,Curiosity13,Curiosity14,Curiosity15) / 30) , 
     "SocialCuriosity" = (sum(Curiosity16,Curiosity17,Curiosity18,Curiosity19,Curiosity20) / 30) , 
     "ThrillSeeking" = (sum(Curiosity21,Curiosity22,Curiosity23,Curiosity24,Curiosity25) / 30) , 
     "NeedforCognition" = (sum(NeedCognition1,NeedCognition2,NeedCognition3,NeedCognition4,NeedCognition5,NeedCognition6,NeedCognition7,NeedCognition9,NeedCognition10,NeedCognition11,NeedCognition12,NeedCognition13,NeedCognition14,NeedCognition15,NeedCognition16,NeedCognition17,NeedCognition18) / 102) , # Removed NeedCognition8,
     "Locomotion" = (sum(SelfRegulation1,SelfRegulation2,SelfRegulation3,SelfRegulation4,SelfRegulation5,SelfRegulation7,SelfRegulation8,SelfRegulation10,SelfRegulation11, SelfRegulation12) / 60) , #Removed SelfRegulation6, SelfRegulation9
     "Assessment" = (sum(SelfRegulation14,SelfRegulation15,SelfRegulation16,SelfRegulation18,SelfRegulation19,SelfRegulation20,SelfRegulation21,SelfRegulation22,SelfRegulation24) / 54) ,   #Removed   `SelfRegulation13`, SelfRegulation17,SelfRegulation23
     "NonConformity"= (sum(NonConformity2,NonConformity3,NonConformity4,NonConformity5,NonConformity7,NonConformity9,NonConformity10) / 42) , # Removed NonConformity1, NonConformity6, NonConformity8,
     "Adaptability"= (sum (Adaptability1,Adaptability2,Adaptability3,Adaptability5,Adaptability6,Adaptability7,Adaptability8) / 42) , #Removed Adaptability4
     "Grit" = (sum (Grit1,Grit3,Grit4,Grit5,Grit6,Grit7,Grit8)/ 42), #Removed Grit 2
     "SelfEfficacy" = (sum (SelfEfficacy1, SelfEfficacy2)/ 14 )) %>%
          select (ID, CyberPro:OtherTraits, SearchforKnowledge:SelfEfficacy) 

#Scoring and development of T Scores based on published norms
dfb <- df %>% group_by(ID) %>%  
     mutate("Skepticism" = (50+10*((sum (Skepticism1,Skepticism2,Skepticism3,Skepticism4,Skepticism5,Skepticism6,Skepticism7, Skepticism8,Skepticism9,Skepticism10,Skepticism11,Skepticism12,Skepticism13,Skepticism14,Skepticism15,Skepticism16,Skepticism17,Skepticism18, Skepticism19,Skepticism20,Skepticism21,Skepticism22,Skepticism23,Skepticism24,Skepticism25,Skepticism26,Skepticism27,Skepticism28, Skepticism29, Skepticism30)-(138.6*6/6))/12.6)), 
     "JoyousExploration" = (50+10*((sum (Curiosity1,Curiosity2,Curiosity3,Curiosity4,Curiosity5) / 5)-(5.25*6/7))/(1.09*6/7)) , 
     "DeprivationSensitivity" = (50+10*((sum (Curiosity6,Curiosity7,Curiosity8,Curiosity9,Curiosity10) / 5) -(4.90*6/7))/(1.14*6/7)), 
     "StressTolerance" = (50+10*((sum (Curiosity11,Curiosity12,Curiosity13,Curiosity14,Curiosity15) / 5) -(4.42*6/7))/(1.36*6/7)), 
     "SocialCuriosity" = (50+10*((sum (Curiosity16,Curiosity17,Curiosity18,Curiosity19,Curiosity20) / 5)-(4.42*6/7))/(1.35*6/7)) , 
     "ThrillSeeking" = (50+10*((sum (Curiosity21,Curiosity22,Curiosity23,Curiosity24,Curiosity25) / 5)-(3.88*6/7))/(1.32*6/7)) , 
     "NeedforCognition" = (50+10*((sum(NeedCognition1,NeedCognition2,NeedCognition3,NeedCognition4,NeedCognition5,NeedCognition6,NeedCognition7,NeedCognition8,NeedCognition9,NeedCognition10,NeedCognition11,NeedCognition12,NeedCognition13,NeedCognition14,NeedCognition15,NeedCognition16,NeedCognition17,NeedCognition18) / 18)-(3.64*6/5))/(.695*6/7)), 
     "Locomotion" = (50+10*((sum(SelfRegulation1,SelfRegulation2,SelfRegulation3,SelfRegulation4,SelfRegulation5,SelfRegulation6,SelfRegulation7,SelfRegulation8,SelfRegulation9,SelfRegulation10,SelfRegulation11, SelfRegulation12) / 12 )-(4.14*6/6))/.69) , 
     "Assessment" = (50+10*((sum(`SelfRegulation13`,SelfRegulation14,SelfRegulation15,SelfRegulation16,SelfRegulation17,SelfRegulation18,SelfRegulation19,SelfRegulation20,SelfRegulation21,SelfRegulation22,SelfRegulation23,SelfRegulation24) / 12)-(3.92*6/6))/.75),      "NonConformity"= (50+10*((sum(NonConformity1,NonConformity2,NonConformity3,NonConformity4,NonConformity5,NonConformity6,NonConformity7,NonConformity8,NonConformity9,NonConformity10) / 10)-(2.51*6/5))/(.470*6/5)) , 
     "Adaptability"= (50+10*((sum (Adaptability1,Adaptability2,Adaptability3,Adaptability4,Adaptability5,Adaptability6,Adaptability7,Adaptability8) / 8)-(3.60*6/5))/(.539*6/5)),
     "Grit" = (50+10*((sum (Grit1,Grit2,Grit3,Grit4,Grit5,Grit6,Grit7,Grit8)/ 8)-(3.65*6/5))/(.73*6/5))  ) %>%
          select (ID, CyberPro:OtherTraits, Skepticism:Grit) 

#Summary DataFrame
df2a <- dfa %>% 
     gather(SearchforKnowledge:SelfEfficacy, key=Dimension, value=Score) %>% 
     mutate(Category=if_else(Dimension %in% c("SearchforKnowledge", "SuspensionofJudgement", "SelfDetermining", "InterpersonalUnderstanding", "SelfConfidence", "QuestioningMind"), "Skepticism",
          if_else(Dimension %in%  c("JoyousExploration", "DeprivationSensitivity", "StressTolerance", "SocialCuriosity", "ThrillSeeking"), "Curiosity", 
          if_else(Dimension=="NeedforCognition", "NeedforCognition",
          if_else(Dimension == "Locomotion", "Locomotion",
          if_else (Dimension=="Assessment", "Assessment",
          if_else(Dimension == "Adaptability", "Adaptability", if_else(Dimension == "NonConformity", "NonConformity", if_else(Dimension=="Grit", "Grit", "SelfEfficacy" )))))))))

df2b <- dfb %>% 
     gather(Skepticism:Grit, key=Dimension, value=Score) %>% 
     mutate(Category=if_else(Dimension=="Skepticism", "Skepticism",
          if_else(Dimension %in%  c("JoyousExploration", "DeprivationSensitivity", "StressTolerance", "SocialCuriosity", "ThrillSeeking"), "Curiosity", 
          if_else(Dimension=="NeedforCognition", "NeedforCognition",
          if_else(Dimension == "Locomotion", "Locomotion",
          if_else (Dimension=="Assessment", "Assessment",
          if_else(Dimension == "Adaptability", "Adaptability", if_else(Dimension == "NonConformity", "NonConformity", if_else(Dimension=="Grit", "Grit", "Other" )))))))))                            
######Respondant Background
#count of respondants
n_CyberPro <- df %>% filter(CyberPro=="Yes") %>% count(CyberPro) 
n_Not_CyberPro <- df %>% filter (CyberPro=="No") %>% count(CyberPro) 

#Education
df_ed <-df %>% select(Education) 
df_ed$Education<- gsub("\\(", "", df_ed$Education)
df_ed$Education<- gsub("\\)", "", df_ed$Education)
df_ed2<-df_ed %>% 
     separate(col = `Education`, into=c("Education", "Field"), sep = "_", remove = "TRUE") %>% 
     na.omit(df_ed) %>% 
     group_by(Education) %>% summarise(n=n()/n_CyberPro$n)

df_ed3<-df_ed %>% separate(Education, c("Education1", "Education2", "Education3", "Education4"), sep=",") %>%
     gather(Education1:Education4, key=Category, value=Education) %>% select (-Category ) %>% 
     separate(col = `Education`, into=c("Education", "Field"), sep = "_", remove = "FALSE") %>% 
     na.omit(df_ed) %>% 
     group_by(Field) %>% summarise(n=n()/n_CyberPro$n) %>% filter(Field=="CS or Related")


#Certifications
df_cert <-df %>% select(Certifications) 
df_cert$Certifications<- gsub("\\(", "", df_cert$Certifications)
df_cert$Certifications<- gsub("\\)", "", df_cert$Certifications)
df_cert2<-df_cert %>% separate(Certifications, c("Certifications1", "Certifications2", "Certifications3", "Certifications4", "Certifications5", "Certifications6", "Certifications7", "Certifications8", "Certifications9"), sep=",") %>%
     gather(Certifications1:Certifications9, key=Category, value=Certifications) %>% select (-Category ) %>% 
     na.omit(df_cert)

df_cert3 <- df_cert2 %>% group_by(Certifications) %>% summarise(n=n())
 
#Hobbies
df_hobby <-df %>% select(Hobbies) 
df_hobby$Hobbies<- gsub("\\(", "", df_hobby$Hobbies)
df_hobby$Hobbies<- gsub("\\)", "", df_hobby$Hobbies)
df_hobby2<-df_hobby %>% separate(Hobbies, c("Hobbies1", "Hobbies2", "Hobbies3", "Hobbies4", "Hobbies5", "Hobbies6", "Hobbies7", "Hobbies8"), sep=",") %>%
     gather(Hobbies1:Hobbies8, key=Category, value=Hobbies) %>% select (-Category ) %>% 
     na.omit(df_hobby) 
#df_hobby3 <- df_hobby2 %>%  group_by(Hobbies) %>% summarise(n=n())

#Check on Distribution of Results 
#df2 %>% ggplot(aes(sample=Score), color="lightgreen") +  # Create QQplot with ggplot2 package
 # stat_qq(col="green") +
  #stat_qq_line(col = "red") +facet_wrap(Dimension~.)

#K means clustering
set.seed(100)

dfclustera <- dfa %>% select (ID,SearchforKnowledge:Grit)
dfclustera<- data.frame(dfclustera, row.names=1)
myclustersa <- kmeans(dfclustera, centers = 3, nstart = 25)
dfclustera <- data.frame(dfclustera) %>% cbind(myclustersa$cluster)
dfclustera <- dplyr::rename(dfclustera, cluster = `myclustersa$cluster`) 


dfclusterb <- dfa %>% select (ID,JoyousExploration:ThrillSeeking)
dfclusterb<- data.frame(dfclusterb, row.names=1)
myclustersb <- kmeans(dfclusterb, centers = 4, nstart = 25)
dfclusterb <- data.frame(dfclusterb) %>% cbind(myclustersb$cluster)
dfclusterb <- dplyr::rename(dfclusterb, cluster = `myclustersb$cluster`) 
```

#### `r n_CyberPro$n` Northrop Grumman Cybersecurity Professionals participated in this data collection and `r n_Not_CyberPro$n` other Professionals (ex. Northrop Grumman Program Managers, Systems Engineers).
##### Research aims: 
* Identify personality traits that are common among Northrop Grumman's Cybersecurity Professionals
* Determine raw score distributions or density functions of 17 select personality dimensions; understand variability among those in cybersecurity work roles
* Verify factor analysis of 17 measures (degree individual questions are measuring the intended personality trait)
* Identify potential components (personality traits) to a predictive model of latent talent for cybersecurity work roles 
* Collect respondent feedback on the personality questionnaire 

##### Results and analysis from this data collection will also assist Northrop Grumman Project Work in support of Army Research and the Army Cyber Proponent.

## Education Column Plot
##### Highest degree of Northrop Grumman Cybersecurity Professionals.  `r round(df_ed3$n, 2)*100` percent have degrees in Computer Science or CS related fields. 

```{r message=FALSE, warning=FALSE, echo=FALSE}
df_ed2$Education <- factor(df_ed2$Education, levels = c ("Secondary", "Associates", "Bachelors", "Masters", "PhD"))
df_ed2 %>% ggplot() + 
  geom_col(aes(x=Education, y=n), fill="lightgreen", color="darkgray")  + 
  ylab("Percentage of Participants") +
  geom_text(aes( x=Education, y=n, label = round(n, 2), ),color="black", vjust= -.1, hjust = .1, size=3.5) +
  xlab ("") +
  theme(legend.title= element_text(color="black", size=10), legend.position = "blank") 
#+     facet_grid(.~Field)
  
```

## Experience Histogram
##### Northrop Grumman Cybersecurity Professionals reported, on average, `r df$YearsExperience %>% mean(na.rm=TRUE) %>% round(0)` years years of experience.

```{r message=FALSE, warning=FALSE, echo=FALSE}
df %>% filter(CyberPro=="Yes") %>%  ggplot() + 
  geom_histogram(aes(x=YearsExperience),binwidth = 4, fill="lightblue", color="darkgray")  +
  scale_x_continuous(expand = c(0,0),limits = c(0,35)) +
  geom_vline(xintercept = 11) + 
  geom_text(aes(x=11, y=0), nudge_x=1.1,label="mean (11 years)") +
  xlab("Years of Experience")

#summary(df$YearsExperience)
```

## Certifications Word Cloud
##### Northrop Grumman Cybersecurity Professionals reported, on average, 2-3 certifications.  

```{r message=FALSE, warning=FALSE, echo=FALSE}
#Create a vector containing only the text
text <- df_cert2$Certifications # Create a corpus  
docs <- Corpus(VectorSource(text))
docs <- docs %>%
  tm_map(stripWhitespace)
docs <- tm_map(docs, content_transformer(tolower))
docs <- tm_map(docs, removeWords, stopwords("english"))
dtm <- TermDocumentMatrix(docs) 
matrix <- as.matrix(dtm) 
words <- sort(rowSums(matrix),decreasing=TRUE) 
df_text <- data.frame(word = names(words),freq = words)

wordcloud(words = df_text$word, freq = df_text$freq, min.freq=1, scale=c(7,1), random.order=FALSE, random.color=FALSE, rot.per=0, 
          colors=brewer.pal(8, "Dark2"))

```

## Hobbies Word Cloud
##### Hobbies reported by Northrop Grumman Cybersecurity Professionals.

```{r message=FALSE, warning=FALSE, echo=FALSE}
#Create a vector containing only the text
text2 <- df_hobby2$Hobbies# Create a corpus  

docs2 <- Corpus(VectorSource(text2))
docs2 <- docs2 %>%
  #tm_map(removeNumbers) %>%
  tm_map(removePunctuation) %>%
  tm_map(stripWhitespace)
docs2 <- tm_map(docs2, content_transformer(tolower))
docs2 <- tm_map(docs2, removeWords, stopwords("english"))
dtm2 <- TermDocumentMatrix(docs2) 
matrix2 <- as.matrix(dtm2) 
words2 <- sort(rowSums(matrix2),decreasing=TRUE) 
df_text2 <- data.frame(word = names(words2),freq=words2)

wordcloud(words = df_text2$word, freq = df_text2$freq, scale=c(3, 1), min.freq=1, random.order=FALSE, random.color=FALSE, rot.per=0, 
          colors=brewer.pal(3, "Dark2" ))
```

## Personality Trait Raw Scores
##### Northrop Grumman Cybersecurity Professionals' trait raw scores are displayed as density plots.

```{r message=FALSE, warning=FALSE, echo=FALSE}
df2a %>% filter(Dimension != "SelfEfficacy", CyberPro=="Yes") %>% 
  ggplot() +
  geom_density(aes(x=Score), fill="lightgreen") +
  facet_wrap(Dimension~., ncol=4) + geom_vline(aes(xintercept=.50)) +
  xlim (0,1) +
  xlab ("Raw Score Normalized")

```

##### The description of each personality dimension is at the bottom of this page.  *NonConformity* appears to be least important in this sample and has limited variability around the center of this scale. 

## Personality Traits and Experience Correlations
##### Data analysis determined several moderate correlations (0.3 - 0.5) between behavioral traits and years of experience.

```{r message=FALSE, warning=FALSE, echo=FALSE}
dfc <- dfa %>% 
     filter(CyberPro=="Yes") %>% 
     select(YearsExperience, ID,YearsExperience, SearchforKnowledge:SelfEfficacy)

dfc <- column_to_rownames(dfc, "ID")

Correlation3 <- as.data.frame(cor(dfc))
Correlation3 <- rownames_to_column(Correlation3, "Category") 
Correlation3 <- Correlation3 %>% filter(Category=="YearsExperience") %>% gather(SearchforKnowledge:SelfEfficacy, key=Category, value=Correlation) %>%  mutate(CorrStrength=if_else(abs(Correlation)>.45, "Strong", if_else(abs(Correlation)>.25, "Moderate", if_else(abs(Correlation)>.1, "Weak", "None"))))

Correlation3 %>% filter (Correlation>.2 | Correlation <.2) %>% 
     mutate(Category = fct_reorder(Category, Correlation, .fun='median'))%>% 
     ggplot(aes(x=Category, y=Correlation, fill=CorrStrength)) + 
     geom_col() + 
     scale_fill_manual(values=c("lightgreen", "darkgray", "darkgray")) +
     geom_text(aes(label = round(Correlation, 1)),color="black", vjust= -.1, hjust = 1, size=3.5) +
     theme(legend.title= element_text(color="black", size=10), legend.position = "blank") +
     xlab("") +
     coord_flip() 
```

##### Positive Correlations with Years of Experience
* *Self-Efficacy*:  belief in one's own ability to deal with a prospective situation in cybersecurity roles.
* *SelfConfidence*:  Someone who would be unafraid to pursue a resolution when he/she uncovers a questionable activity.
* *SelfDetermining*:  Taking a step back from an issue, position, or posture and asking "does this make sense to me?"
* *StressTolerance*: Ability to cope win the anxiety inherent in confronting the new, unexpected, complex, mysterious, and obscure events.

##### Negative Correlations with Years of Experience
* *Assessment*: focus on self-evaluation and "doing the right thing."
* *DeprivationSensitivity*: Seeking information to escape the tension of not knowing something.  Intellectually engaged to think about abstract or complex ideas and solve problems.


## Self-Efficacy Correlations
#####  Northrop Grumman Cybersecurity and Non-cybersecurity respondents rated self-efficacy for "the level of knowledge" and "the ability" to work in the cybersecurity field".  Several personality dimensions display moderate positive correlations.  

```{r message=FALSE, warning=FALSE,echo=FALSE}
dfd <- dfa %>% 
     filter(CyberPro=="Yes") %>% 
     select(ID, SearchforKnowledge:SelfEfficacy)
dfd <- column_to_rownames(dfd, "ID")

Correlation <- as.data.frame(cor(dfd))
Correlation <- rownames_to_column(Correlation, "Category") 
Correlation <- Correlation %>% filter(Category=="SelfEfficacy") %>% gather(SearchforKnowledge:SelfEfficacy, key=Category, value=NG_CyberSecurity)

dfe <- dfa %>% 
    filter(CyberPro=="No") %>% 
     select(ID, SearchforKnowledge:SelfEfficacy)
dfe <- column_to_rownames(dfe, "ID")

Correlation2 <- as.data.frame(cor(dfe))
Correlation2 <- rownames_to_column(Correlation2, "Category") 
Correlation2<- Correlation2 %>% filter(Category=="SelfEfficacy") %>% gather(SearchforKnowledge:SelfEfficacy, key=Category, value=NG_Other)

EfficacyCorrelation <- Correlation %>% left_join(Correlation2) %>% gather(NG_CyberSecurity:NG_Other, key=Group, value=Score) %>% mutate(CorrStrength=if_else(Score>.45, "Strong", if_else(Score>.25, "Moderate", if_else(Score>.1, "Weak", "None"))))
EfficacyCorrelation$CorrStrength <-factor(EfficacyCorrelation$CorrStrength, levels = c("Strong", "Moderate", "Weak", "None"))

EfficacyCorrelation %>% filter (Category != "SelfEfficacy", Score>.2) %>% 
     mutate(Category = fct_reorder(Category, Score, .fun='median'))%>% 
     ggplot(aes(x=Category, y=Score, fill=CorrStrength)) + 
     geom_col() + 
     scale_fill_manual(values=c("green", "lightgreen", "darkgray")) +
     geom_text(aes(label = round(Score, 1)),color="black", vjust= -.1, hjust = 1, size=3.5) +
     theme(legend.title= element_text(color="black", size=10), legend.position = "blank") +
     coord_flip() + facet_grid(.~Group) + xlab("")
```

##### Cybersecurity Professionals: Self-Confidence and Need for Cognition correlated highest
##### Non-cybersecurity Professionals: Joyous Exploration and Stress Tolerance correlated highest

## K Means Clustering I (Curiosity Dimensions)

##### Personality clustering results from respondent data for Curiosity (5 personality dimensions).  The chart below is faceted into four clusters generally described by Kashdan et al. as:
##### Cluster 1: "Empathizers" (`r 100*round(30/102, 2)`%)   
##### Cluster 2: "Fascinated" (`r 100*round(27/102,2)`%) 
##### Cluster 3: "Problem Solvers" (`r 100*round(25/102,2)`%) 
##### Cluster 4: "Avoiders" (`r 100*round(20/102,2)`%) 

```{r message=FALSE, warning=FALSE,echo=FALSE}
###Cluster profiles
dfcluster2b <- dfclusterb %>% gather(JoyousExploration:ThrillSeeking, key=Category, value=Score)
dfcluster2b$cluster<-as.factor(dfcluster2b$cluster)
dfcluster3b<-dfcluster2b %>% group_by(Category, cluster) %>% summarise(Score=mean(Score))
dfcluster3b$cluster<- paste("Cluster", dfcluster3b$cluster) 
df_sd <- dfcluster3b %>% group_by(Category) %>% summarise(sd=sd(Score)) %>% mutate(cluster_sd=if_else(sd>.075, "High", "Low"))
dfcluster3b <- dfcluster3b %>% left_join(df_sd)
dfcluster3b$cluster_sd <- factor(dfcluster3b$cluster_sd)
#myclusters$cluster
#myclusters$centers
#myclustersb$size
#fviz_cluster(myclusters, data = dfcluster)

dfcluster3b %>% ungroup() %>% 
     mutate(Category = fct_reorder(Category, -Score, .fun=mean)) %>% 
     ggplot(aes (x=Category, y=Score)) + 
     geom_col(aes(fill=Category)) +
     scale_fill_manual(values = c("red", "orange", "blue", "green", "purple")) +
        theme(legend.title= element_text(color="white", size=0), legend.position = "top") +
      xlab("") + ylim(0,1) + ylab("Raw Score Normalized") + facet_grid(.~cluster, scales="free_y") +
    theme(axis.title.x=element_blank(),  axis.text.x=element_blank(),  axis.ticks.x=element_blank())
```

##### Read a description of these clusters on pages 13-14 of the following published article:
###### https://www.researchgate.net/profile/Todd_Kashdan/publication/321471978_The_Five-Dimensional_Curiosity_Scale_Capturing_the_bandwidth_of_curiosity_and_identifying_four_unique_subgroups_of_curious_people/links/5ae34644aca272fdaf904f6f/The-Five-Dimensional-Curiosity-Scale-Capturing-the-bandwidth-of-curiosity-and-identifying-four-unique-subgroups-of-curious-people.pdf

## K Means Clustering II (All Personality Dimensions)
##### Personality dimensions were faceted based on variability among clusters (personality dimensions with high variability vs. personality dimensions with low variability). 

```{r message=FALSE, warning=FALSE,echo=FALSE}
dfcluster2a <- dfclustera %>% gather(SearchforKnowledge:Grit, key=Category, value=Score)

dfcluster2a$cluster<-as.factor(dfcluster2a$cluster)

dfcluster3a<-dfcluster2a %>% group_by(Category, cluster) %>% summarise(Score=mean(Score))

dfcluster3a$cluster<- paste("Cluster", dfcluster3a$cluster) 

df_sd <- dfcluster3a %>% group_by(Category) %>% summarise(sd=sd(Score)) %>% mutate(cluster_sd=if_else(sd>.075, "High", "Low"))

dfcluster3a <- dfcluster3a %>% left_join(df_sd)

dfcluster3a$cluster_sd <- factor(dfcluster3a$cluster_sd)

#myclustersa$cluster
#myclustersa$centers
#myclustersa$size
#fviz_cluster(myclusters, data = dfcluster)

dfcluster3a %>% ungroup() %>% 
     mutate(Category = fct_reorder(Category, Score, .fun=max)) %>% 
     ggplot(aes (x=Category, y=Score, group=cluster)) + 
     geom_point(aes(color=cluster), size=2) +
     geom_line(aes(linetype=cluster)) +
     scale_linetype_manual(values = c("blank", "dashed", "blank"))+
     scale_size_manual(values=c("3", "3")) +
     scale_color_manual(values = c("green", "darkgray", "blue")) +
     coord_flip() + 
     theme(legend.title= element_text(color="blue", size=10), legend.position = "top") +
    xlab("") + ylim(0.4,1) + ylab("Raw Score Normalized") + facet_grid(cluster_sd~., scales="free_y")
```

#####  The largest cluster, *Cluster 2* (`r 100*round(44/102,2)`%), generally reports high scores across all the dimensions and appears to resemble "Problem Solvers" and "Fascinated" personality profiles.  
##### *Cluster 1* (`r 100*round(28/102,2)`%) and *Cluster 3* (`r 100*round(30/102,2)`%) , consists of respondents with lower scores on many dimensions and resemble "Avoiders" and "Empathizers", respectively.
##### Low variability was observed between personality clusters in many dimensions.

## Correlation Analysis of Personality Dimensions

```{r message=FALSE, warning=FALSE,echo=FALSE}
corrplot(cor(dfclustera), method="color", order="hclust", type="full", addrect=12, cl.lim=c(-1,1), addCoef.col="black", rect.col="green", diag = FALSE, number.font=1, number.digits = 1, number.cex = .7)
```

##### Correlation coefficients are displayed and shaded.  Green boxes are drawn from the results of hierarchical clustering of these personality dimensions.  For example, respondent data suggests "Search for Knowledge" and "Joyous Exploration" measure the same trait.

## References:
###### Adaptability and Conformity, International Personality Item Pool: A Scientific Collaboratory for the Development of Advanced Measures of Personality Traits and Other Individual Differences. http://ipip.ori.org/
###### Cacioppo, J. T., Petty, R. E., and Kao, C. F. (1984). The efficient assessment of need for cognition. *Journal of Personality Assessment*, 48, 306-307.
###### Duckworth, A. L. & Quinn, P. D. (2009). Development and validation of the Short Grit Scale (Grit-S). *Journal of Personality Assessment*, 91(2), 166-174.
###### Hurt, R. K. (2010, May). Development of a Scale to Measure Professional Skepticism. *Auditing: A Journal of Practice and Theory*, 29(1), 149-171.
###### Kashdan, T. B., Stiksma, M. C., Disabato, D. J., Mcknight, P. E.,, Bekier, J., Kaji, J., Lazarus, R. (2017, December). The Five-Dimension Curiosity Scale: Capturing the bandwidth of curiosity and identifying four unique subgroups of curious people. *Journal for Research in Personality*, 73, 130-149.
###### Kruglanski, A. W., Thompson, E. P., Higgins, E. T., Atash, M. N., Pierro, A., Shah, J. Y., Spiegel, S. (2000, Nov). To "do the right thing" or to "just do it": Locomotion and assessment as distinct self-regulatory imperatives. *Journal of Personality and Social Psychology*, 79(5), 793-815.

#### Definitions of Personality Dimensions
* *SearchforKnowledge*:  Ability to ask questions beyond the obvious answer.
* *StressTolerance*: Ability to cope win the anxiety inherent in confronting the new, unexpected, complex, mysterious, and obscure events.
* *JoyousExploration*: Preference for new information and experiences, and the valuing of self-expansion over security.
* *SelfConfidence*:  Someone who would be unafraid to pursue a resolution when he/she uncovers a questionable activity.
* *InterpersonalUnderstanding*:  Not placing inappropriate degree of trust in people, processes, controls and data.
* *Locomotion*: decisiveness, task orientation, intrinsic motivation to get the job done.
* *SuspensionofJudgement*:  Characteristic of withholding a conclusion on a matter until sufficient evidence to form a basis for a reasonable conclusion has been obtained
* *DeprivationSensitivity*: Seeking information to escape the tension of not knowing something.  Intellectually engaged to think about abstract or complex ideas and solve problems.
* *Need for Cognition*: engage and enjoy effortful cognitive endeavors.
* *SelfDetermining*:  Taking a step back from an issue, position, or posture and asking "does this make sense to me?"
* *Grit*: perseverance and passion for long-term goals.
* *SocialCuriosity*: Desire to know what other people are thinking and doing through overt means (observing and probing questions) or covert means (listening into conversations or gathering second-hand information).
* *QuestioningMind*:  Attitude to look below the surface and see if the numbers, situation, factors or people look out of place.
* *Adaptability*: ability to adjust to new conditions.
* *Assessment*: focus on self-evaluation and "doing the right thing."
* *ThrillSeeking*: On the hunt for varied, novel, complex, and intense experiences and ready to risk physical, social, and financial safety.
* *Non-Conformity*: refusal to conform to prevailing rules or practices.